% -------------------------------------------------------------------------------- %

\begin{exercise}[\textbf{Missing information}]

An investigation of ethnic differences in reports of pain perception
was presented at the annual meeting of the American Psychosomatic Society
(Mar. 2001). A sample of 55 blacks and 159 whites participated in the study.
Subjects rated (on a 13-pointt scale) the intensity and unpleasantness of
pain felt when a bag of ice was placed on their foreheads for two minutes.
(Higher ratings correspond to higher pain intensity.)
A summary of the results is provided in the following table.

\begin{center}
    \begin{tabular}{c|cc}
        & Blacks & Whites \\
        \hline
        Sample Size & 55 & 159 \\
        Mean pain intensity & 8.2 & 6.9
    \end{tabular}
\end{center}

\begin{enumerate}[label = (\alph*)]
    \item Why is it dangerous to draw a statistical inference from the summarized data? Explain.
    \item What values of the missing sample standard deviations would lead
    you to conclude (at $\alpha = 0.05$) that blacks, on average, have
    a higher pain intensity rating than whites?
    \item What values of the missing sample standard deviation would lead
    you to an inconclusive decision (at $\alpha = 0.05$) regarding whether
    blacks or whites have a higher mean intensity rating?
\end{enumerate}

\end{exercise}

% -------------------------------------------------------------------------------- %

\begin{solution}

\phantom{}

\end{solution}

% -------------------------------------------------------------------------------- %
