% -------------------------------------------------------------------------------- %

\begin{exercise}[\textbf{MBA students}]

One way to assess the benefits of an MBA degree is to investigate the salaries
received by MBA students several years after graduation.
In 1998, the Graduate Management Admission Council estimated that the
median earnings of graduates of full-time, highly ranked MBA programs
four years after graduating was \$96000 (Selections, Winter 1999).
A random sample of 50 graduates from the class of 1996 of a particularly
highly ranked MBA program were mailed a questionnaire and asked to report
their earnings for 2000. Fifteen useable responses were received;
9 indicated earnings greater than \$96000 and 6 indicated earnings below
\$96000.

\begin{enumerate}[label = (\alph*)]
    \item Specify the null and alternative hypotheses that should be
    used in testing whether the median income of graduates of the MBA
    program was more than \$96000 in 2000.
    \item Conduct the test of the previous part using $\alpha = 0.05$ and
    draw your conclusions in the context of the problem. 
\end{enumerate}

\end{exercise}

% -------------------------------------------------------------------------------- %

\begin{solution}

\phantom{}

    \begin{enumerate}[label = (\alph*)]
        \item The null hypothesis states that the median income is given by $H_0: M_0 := 96000$,
        while the alternative states $H_1: M > M_0$.
        For our purpose the Sign test is the most fitting test, where our
        test statistic $X \sim_{H_0} \text{Bin}(n, 0.5)$ counts the number
         of observations exceeding $M_0$.
        \item Plugging in the given data we obtain $X = 9, n = 15$.
        Calculating the $p$-value yields

        \begin{align*}
            p-\text{value} = \P(X \geq 9) = \sum_{k=9}^{15}\binom{15}{k}\frac{1}{2^{15}}
            \approx 0.3036194.
        \end{align*}

        Based on these results we cannot reject the null.
    \end{enumerate}

\end{solution}

% -------------------------------------------------------------------------------- %
