\section{Miscellaneous}

\begin{lemma}[Urysohn's Lemma] \label{lemma:Urysohn} \cite[p. 445]{Ana1&2}
	If $A$ and $B$ are two closed and disjoint sets of an object $\tspace$ of $\Normal$, then there exists an $f \in \Hom_\Normal\pbraces{\tspace, \pbraces{[0,1], \eucl}}$ such that $f\bbraces{A} \subseteq \{0\}$ and $f\bbraces{B} \subseteq \{1\}$. 
\end{lemma}


\begin{definition}
	Let $\tspace$ be an object of $\Top$. A set $\cover$ of subsets of $X$ is called a \textit{cover} of $X$, if and only if $\bigcup \cover = X$. The cover $\cover$ of $X$ is said to be an \textit{open cover} of $\tspace$, if and only if $\cover \subseteq \mathcal{T}$. The cover $\cover$ of $X$ is said to be \textit{locally finite}, if and only if for every $x \in X$ there exists a neighbourhood $W$ of $x$ in $\tspace$ such that the set $\Bbraces{U \in \cover\mid U \cap W \neq \emptyset}$ is finite. A cover $\cover[V]$ of $X$ is called a \textit{refinement} of $\cover$, if and only if for every $V \in \cover[V]$ there exists a $U \in \cover$, such that $V \subseteq U$. 
\end{definition}

\begin{definition}
	A topological space $\tspace$ is called \textit{paracompact}, if and only if every open cover of $\tspace$ has a locally finite, open refinement that covers $\tspace$. 
\end{definition}

\begin{theorem}\label{theorem:stone}
	Every metrizable space is paracompact. \cite{Top}
\end{theorem}

\begin{lemma} \label{lemma:locally_finite_system} \cite[p. 63]{Top}
	If $\mathcal{A}$ is a locally finite set-system of some topological space $\tspace$, then
	\begin{align*}
		\cl{\bigcup \mathcal{A}} = \bigcup \cl{\mathcal{A}}.
	\end{align*}
\end{lemma}

\begin{lemma} \label{lemma:para_separation} \cite[p. 71]{Top}
	Let $\tspace$ be a topological space and $A$ and $B$ two closed subspaces of $\tspace$. If 
	\begin{align*}
		\forall x \in B\exists U, V \in \mathcal{T}\pbraces{A \subseteq U \land x \in V \land U \cap V = \emptyset},
	\end{align*}
	then $A$ and $B$ are separated by neighbourhoods. 
\end{lemma}
\begin{proof}
	The proof depends on \ref{lemma:locally_finite_system}.
\end{proof}

\begin{corollary} \label{corollary:para_is_normal} \cite[p. 72]{Top}
	Every paracompact object of $\Haus$ is also an object of $\Normal$. 
\end{corollary}
\begin{proof}
	The proof depends on \ref{lemma:para_separation}.
\end{proof}

\begin{lemma} \label{lemma:special_cover}
	If $\cover$ is a locally finite, open cover of a Hausdorff space $\tspace$ which is paracompact, then for every $U \in \cover$ there exists $V_U \in \mathcal{T}$ such that $\cl{V_U} \subseteq U$ and $\cover[V] := \Bbraces{V_U \mid U \in \cover}$ is a cover of $X$.  
\end{lemma}
\begin{proof}
	Let $\cover[W]$ be the set of all open sets in $\tspace$ meeting only finitely many elements of $\cover$ and whose closure in $\tspace$ is contained in some element of $\cover$.
	
	We claim that $\cover[W]$ is an open cover of $\tspace$. Consider any point $x \in X$. Since $\cover$ is a locally finite cover of $\tspace$, there exists $V \in \mathcal{T}$ containing $x$ that meets only finitely many elements of $\cover$ and there exists $U^\prime \in \cover$, such that $x \in U^\prime$. Since $\tspace$ is an object of $\Normal$ by \ref{corollary:para_is_normal} and $\tspace$ is a Hausdorff space, we find $U \in \mathcal{T}$ such that $x \in U$ and $\cl{U} \subseteq U^\prime$. The set $W := U \cap V$ contains $x$ and is contained in $\cover[W]$. Therefore, $\cover[W]$ is an open cover of $\tspace$. 
	
	Since $\tspace$ is paracompact, there exists a locally finite, open refinement $\cover[W]^\prime$ of $\cover[W]$ that covers $\tspace$. For every $U \in \cover$, we define
	\begin{align*}
		V_U := \bigcup \Bbraces{W^\prime \in \cover[W]^\prime \mid \cl{W^\prime} \subseteq U}.
	\end{align*}
	
	We will show that the set $\cover[V] := \Bbraces{V_U \mid U \in \cover}$ is as desired. In order to prove this we consider any arbitrary point $x \in X$. Since $\cover[W]^\prime$ is a cover of $X$, there exists $W^\prime \in \cover[W]^\prime$ such that $x \in W^\prime$. Since $\cover[W]^\prime$ is a refinement of $\cover[W]$, there is $W \in \cover[W]$ such that $W^\prime \subseteq W$. By definition of $\cover[W]$, there exists $U \in \cover$ such that $\cl{W} \subseteq U$. We obtain $\cl{W^\prime} \subseteq \cl{W} \subseteq U$, hence $x \in V_U$. Therefore, $\cover[V]$ is a cover of $X$. We also observe that $\cover[V] \subseteq \mathcal{T}$. 
	
	Since $\cover[W]^\prime$ is locally finite, we can apply \ref{lemma:locally_finite_system} and obtain
	\begin{align*}
		\cl{V_U} = \bigcup \Bbraces{\cl{W^\prime} \mid W^\prime \in \cover[W] \land \cl{W^\prime} \subseteq U} \subseteq U.
	\end{align*}
	This concludes the proof.
\end{proof}

\begin{theorem}[Stone's coincidence thoerem] \label{theorem:stone_coi} \cite[p. 77]{Top}
	If $\tspace$ is an object of $\Top$ that fulfills \ref{axiom:t1}, then the following statements are equivalent.
	\begin{enumerate}
		\item The topological space $\tspace$ is an object of $\Haus$ and is paracompact.
		
		\item Every open cover of $\tspace$ has an open, barycentric refinement that covers $X$. 
		
		\item Every open cover of $\tspace$ has an open star refinement that covers $X$. 
		
		\item The topological space $\tspace$ fulfills \ref{axiom:t3} and every open cover of $\tspace$ has an open, $\sigma$-discrete refinement that covers $X$.
	\end{enumerate}
\end{theorem}

Our next goal is to extend \ref{theorem:stone_coi} by one more equivalence. This will be achieved by \ref{theorem:para_part}.

\begin{definition}
	Let $\tspace$ be a topological space. A set $\partition \in \Hom_\Top\pbraces{\tspace, \pbraces{[0,1], \eucl}}$ is called a \textit{partition of unity}, if and only if for every $x \in X$ the equality $\sum_{f \in \partition} f(x) = 1$ holds true. This partition of unity $\partition$ is said to be \textit{subordinate} to a cover $\cover$ of $X$, if and only if for every $f \in \partition$ there is a $U \in \cover$ such that $\supp f \subseteq U$. The partition of unity $\partition$ is called \textit{locally finite}, if and only if for every $x \in X$ there exists a neighborhood $V$ of $x$ such that the set $\Bbraces{f \in \partition \mid V \cap \pbraces{\supp f} \neq \emptyset}$ is finite.
\end{definition}

\begin{lemma}\label{lemma:part_to_para}
	If $\partition$ is a locally finite partition of unity of a topological space $\tspace$, then $\cover := \Bbraces{\supp f \mid f \in \partition}$ is a locally finite, open cover of $\tspace$. 
\end{lemma}
\begin{proof}
	We first show that $\partition$ consists of open sets. The set $(0,1]$ is an open set in $\pbraces{[0,1], \eucl}$. Since for any $f \in \partition$ we clearly have $\supp f = f^{-1}\bbraces{(0,1]}$ and $f \in \Hom_\Top\pbraces{\tspace, \pbraces{[0,1], \eucl}}$, the set $\partition$ consists of open sets. 
	
	In order to show that $\partition$ is a cover of $X$, consider any arbitrary $x \in X$. Since 
	\begin{align*}
		\sum_{f \in \partition} f(x) = 1,
	\end{align*}
	there exists $g \in \partition$ such that $g(x) > 0$. Therefore, $x \in \supp g$ and by definition we have $\supp g \in \cover$. 
	
	Finally, we want to show that $\cover$ is locally finite. Consider some $x \in X$. Since $\partition$ is a locally finite partition of unity, there is a neighborhood $V$ of $x$, such that $\Bbraces{f \in \partition \mid V \cap \pbraces{\supp f} \neq \emptyset}$ is finite. Hence, $V$ only meets a finite number of elements of $\cover$. 
\end{proof}

\begin{theorem}\label{theorem:para_part}
	An object $\tspace$ of $\Haus$ is paracompact, if and only if every open cover $\cover$ of $\tspace$ admits a locally finite partition of unity which is subordinate to $\cover$.  
\end{theorem}
\begin{proof}
	First we will proof sufficiency. Let $\cover$ be any open cover of a paracompact Hausdorff space $\tspace$ and $\cover[V]$ a locally finite open refinement of $\cover$ that covers $\tspace$. By \ref{lemma:special_cover}, for every $V \in \cover[V]$ there exists $W_V \in \mathcal{T}$ such that $\cl{W_V} \subseteq V$ and $\cover[W] := \Bbraces{W_V \mid V \in \cover[V]}$ is a cover of $X$. 
	
	The topological space $\tspace$ is an object of $\Normal$ by \ref{corollary:para_is_normal}. Hence, we can pick any $V \in \cover[V]$ and apply \ref{lemma:Urysohn} in order to obtain $f_V \in \Hom_\Top\pbraces{\tspace, \pbraces{[0,1], \eucl}}$ such that $f_V\bbraces{\cl{W_V}} \subseteq \{1\}$ and $\supp f_V \subseteq V$.
	
	We claim that for any $U \in \cover[V]$ the function
	\begin{align*}
		g_U := f_U \pbraces{\sum_{V \in \cover[V]} f_V}^{-1}
	\end{align*}
	is well defined. In order to prove this statement, consider any arbitrary point $x \in X$.  Since $\cover[V]$ is locally finite, there exists a neighborhood $N$ of $x$ such that $\cover[V]^\prime := \Bbraces{V \in \cover[V] \mid N \cap V \neq \emptyset}$ is a finite set.  We obtain for any arbitrary $y \in N$ that
	\begin{align*}
		\sum_{V \in \cover[V]} f_V(y) = \sum_{V \in \cover[V]^\prime} f_V(y) \in [0, \infty).
	\end{align*}
	The function $\sum_{V \in \cover[V]} f_V$ restricted to $N$ is continuous, because it is a finite sum of continuous functions. Since $N$ is a neighborhood of $x$, the sum is also continuous on $X$.
	
	Since $\cover[W]$ is a cover of $X$, there is $\tilde{V} \in \cover[V]$ such that $x \in W_{\tilde{V}}$. Therefore, $0 < f_{\tilde{V}}(x) \leq \sum_{V \in \cover[V]} f_V(x)$. In total we have shown that for every $x \in X$ we have $\sum_{V \in \cover[V]} f_V(x) \in (0, \infty)$. Therefore $g_U$ is well defined.
	
	We easily observe that for every $x \in X$ we have $\sum_{U \in \cover[V]} g_U(x) = 1$. 
	
	Let us now show necessity in the theorem. In order to do this, consider any open cover $\cover$ of $\tspace$. By assumption, there exists a locally finite partition of unity $\partition$ which is subordinate to $\cover$. The set $\cover[V] := \Bbraces{\supp f \mid f \in \partition}$ is by \ref{lemma:part_to_para} a locally finite, open cover of $\tspace$. Since $\partition$ is a partition of unity subordinate to $\cover$, we conclude the proof with the observation that $\cover[V]$ is a refinement of $\cover$. 
\end{proof}
